Unified Understanding of the Dielectric Nature of Two-Dimensional Materials

### 2018-10-30 paper.tex
Add paragraph discussing the 2D and 3D anisotropy

Although we have extensively shown that the treatment for the
dielectric nature differs in 2D (polarizability) and 3D (dielectric
constant) scenarios, a general picture of the dielectric properties in
both dimensions can still be drawn by studying the dielectric
anisotropy. The dielectric anisotropy index $\eta$ is defined as:
\begin{equation}
  \label{eq:anisotropy}
  \begin{aligned}[t]
    \eta =
    \begin{cases}
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\varepsilon^{ii}}{\varepsilon^{jj}}\right)},
      \ \mathrm{Bulk\ Materials}\\
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\alpha^{ii}}{\alpha^{jj}}\right)},
      \ \mathrm{2D\ Materials}\\
    \end{cases}
  \end{aligned}
\end{equation}
$\eta=1$ indicates the material has isotropic dielectric properties
while $\eta \to 0$ means the dielectric property is highly
anisotropic. Figure XX \todo{TBD} shows the phase diagram of $\eta$ as
function of $E_{\mathrm{g}}$ for 2D materials and their bulk
counterparts. Interestingly, the 2D materials (\todo{marker shape})
can be clearly distinguished from the layered bulk materials
(\todo{marker shape}). The boundary separating the 2D and layered bulk
materials is determined using an least-square support vector machine
(LS-SVM) classification algorithm, and can be linearly approximated by
the equation \todo{TBD}. The much lower $\eta$ values of 2D materials
compared with their bulk counterparts indicates a high dielectric
anisotropy, which is responsible for the unique 2D optoelectronic
properties, such as electrostatic transparency
\cite{Liluhua_2014,Tian_2016,Li_2018} and large exciton binding energy
\cite{Pulci_2014,Tran_2014,Chernikov_2014_EB_MoS2_2D3D,Berkelbach_2013}. We
also observe that $\eta$ of 2D materials increase almost linearly with
$E_{\mathrm{g}}$, while such trend is absent for layered bulk
materials. The observations above can be explained by the principles
presented in thie work. As a result from the limited layer thickness
(mostly 3--10 \AA{}), $\alpha^{\perp}$ of a monolayer 2D material
varies much less than $\alpha^{\parallel}$ (Figure \ref{fig-3}b and
\ref{fig-3}c), which explains the domination of $E_{\mathrm{g}}$ in
$\eta$ of 2D materials. On the other hand, the fact that
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ is generally larger than the
values calculated from $\alpha^{\perp}$ of monolayer due to interlayer
coupling (Figure \ref{fig-4}c), gives rise to larger $\eta$ for
layered bulk materials compared with the corresponding monolayer, and
making it possible to separate the 2D and layered bulk materials from
the $\eta-E_{\mathrm{g}}$ phase diagram.

@@

>>>>

Although we have extensively shown that the treatment for the
dielectric nature differs in 2D (polarizability) and 3D (dielectric
constant) scenarios, a general picture of the dielectric properties in
both dimensions can still be drawn by studying the dielectric
anisotropy. The dielectric anisotropy index $\eta$ is defined as:
\begin{equation}
  \label{eq:anisotropy}
  \begin{aligned}[t]
    \eta =
    \begin{cases}
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\varepsilon^{ii}}{\varepsilon^{jj}}\right)},
      \ \mathrm{Bulk\ Materials}\\
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\alpha^{ii}}{\alpha^{jj}}\right)},
      \ \mathrm{2D\ Materials}\\
    \end{cases}
  \end{aligned}
\end{equation}
$\eta=1$ indicates the material has isotropic dielectric properties
while $\eta \to 0$ means the dielectric property is highly
anisotropic. Figure \ref{fig:aniso} shows the phase diagram of $\eta$
as function of $E_{\mathrm{g}}$ for 2D materials and their bulk
counterparts. Interestingly, the 2D materials (blue triangle) can be
clearly distinguished from the bulk layered materials (orange
square). The boundary separating the 2D and layered bulk materials is
determined using an linear support vector machine (SVM) classification
algorithm to be $y=0.048x+0.087$. The much lower $\eta$ values of 2D
materials compared with their bulk counterparts indicates a high
dielectric anisotropy, which is responsible for the unique 2D
optoelectronic properties, such as electrostatic transparency
\cite{Liluhua_2014,Tian_2016,Li_2018} and large exciton binding energy
\cite{Pulci_2014,Tran_2014,Chernikov_2014_EB_MoS2_2D3D,Berkelbach_2013}. We
also observe that $\eta$ of 2D materials increase almost linearly with
$E_{\mathrm{g}}$, while such trend is absent for layered bulk
materials. The observations above can be explained by the principles
presented in thie work. As a result from the limited layer thickness
(mostly 3--10 \AA{}), $\alpha^{\perp}$ of a monolayer 2D material
varies much less than $\alpha^{\parallel}$ (Figure \ref{fig-3}b and
\ref{fig-3}c), which explains the domination of $E_{\mathrm{g}}$ in
$\eta$ of 2D materials. On the other hand, the fact that
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ is generally larger than the
values calculated from $\alpha^{\perp}$ of monolayer due to interlayer
coupling (Figure \ref{fig-4}c), gives rise to larger $\eta$ for
layered bulk materials compared with the corresponding monolayer, and
making it possible to separate the 2D and layered bulk materials from
the $\eta-E_{\mathrm{g}}$ phase diagram. For comparison, we also
superimpose the dielectric anisotropy $\eta$ of common semiconducting
materials in other dimensions (details see Supplementary Section SXX
\todo{TBD}) on the phase diagram in Figure \ref{fig:aniso}. Bulk
covalent materials (3D, e.g. GaN) and fullerenes (0D, e.g. C$_{60}$)
show isotropic dielectric property, scattered on the line $\eta=1$. On
the other hand, reduced dimensionality increases the dielectric
anisotropy of materials such as planar organic semiconductor (OSc,
1D-2D, e.g. CuPc), carbon nanotube (CNT, 1D) and linear OSc (0D-1D,
e.g. polyacene). Interestingly, these materials also scatter along the
boundary line $y=0.048x+0.087$, indicating the criteria distinguishing
2D (more anisotropic) and bulk layered materials (more isotropic) from
the $\eta-E_{\mathrm{g}}$ diagram, can also be applied to other
dimensions. From the phase diagram, we can see that 2D and bulk
layered materials (also including 2D van der Waals heterostructure
(vdWH) \cite{Novoselov_2016}), provides more flexibility in
controlling the dielectric and electronic properties, compared with semiconductors in other dimensions.

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/fig5.pdf}
  \caption{\textbf{Phase diagram of dielectric anisotropy $\eta$ as
      function of bandgap $E_{\mathrm{g}}$}. The
    $\eta$-$E_{\mathrm{g}}$ values of 2D materials (blue triangle) and
    their bulk counterparts (orange square) can be distinguished by
    the line $y=0.048x+0.087$. $\eta-E_{\mathrm{g}}$ values of
    semiconducting materials in other dimensions are also superimposed
    for comparison. Isotropic dielectric property is observed for bulk
    covalent materials (3D, red triangle) and fullerenes (0D, green
    star), while reduced dimensional materials, including planar
    organic semiconductor(OSc, 1D-2D, brown triangle), carbon nanotube
    (CNT, magenta circle) and linear OSc (0D-1D, violet pentagon) are
    scattered along the boundary line. The dimensionality and
    structure of typical materials are shown along the axis on the
    right. Compared with other materials, 2D materials and their bulk
    counterparts provide more flexibility of controlling the
    dielectric anisotropy.}
  \label{fig:aniso}
\end{figure}
